---
title: "Interactive Graphics"
subtitle: "Plotly, Leaflet, and (mostly) Shiny"
author: "Susan Vanderplas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  xaringan::moon_reader:
    css: ["default", "template/unl.css"]
    lib_dir: libs
    includes:
      in_header: template/header.html
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(echo = T, 
  fig.path = "deps/interactive/",
  message = F, warning = F, 
  fig.width = 8, fig.height = 6, 
  out.width = "100%")
```

class:inverse,middle,center
# Plotly

---
## Plotly

```{r penguin-plotly-box, eval = F}
library(palmerpenguins)
library(tidyverse)
library(plotly)

p <- penguins %>%
  ggplot(aes(x = species, y = body_mass_g)) + 
  geom_boxplot() + 
  coord_flip()
ggplotly(p)

```

---
## Plotly

```{r penguin-plotly-box, echo = F, eval = T}
```

---

## Interactivity in Plotly

- Predetermined user interactivity

- Precomputed output

- Zoom, filter, details-on-demand, mouseover

- With JS skills, linked plots


---
class:inverse,middle,center
# Leaflet

---

## Leaflet

```{r leaflet-bridges, eval = F}
library(leaflet)
# Tidy tuesday: Baltimore bridges
bridges <- readr::read_csv('https://bit.ly/3jyMXm7') %>% 
  mutate(color = str_replace_all(bridge_condition,
                                 c("Fair" = "orange", 
                                   "Good" = "yellow", 
                                   "Poor" = "red"))) 

bridges %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(~long, ~lat, color = ~color, 
                   radius = 3, stroke = F, fillOpacity = 0.5)
```

---

## Leaflet


```{r leaflet-bridges, echo = F, eval = T}
```

---

## Leaflet

```{r leaflet-bridges2}
bridges %>% leaflet() %>%
  addTiles(
    "https://server.arcgisonline.com/ArcGIS/rest/services/World_Imagery/MapServer/tile/{z}/{y}/{x}"
  ) %>% 
  addCircleMarkers(~long, ~lat, color = ~color)
```


---

## Interactivity in Leaflet

- Mouseover

- Zoom in

- Filter

- With JS skills, linked plots

---
class:inverse,middle,center
# Shiny

.bottom[Slides modified from [Stat 585 at Iowa State](https://stat585-at-isu.github.io/materials-2019/10_interactive/01_shiny.html)]

---

## What is `shiny`?

- `shiny` is an R package that allows us to easily create interactive web applets using R. 

- Produced by RStudio: http://shiny.rstudio.com

- Code can be entirely in R (or customized with HTML/JavaScript)

- RStudio's showcase gallery of Shiny applets: http://shiny.rstudio.com/gallery/

---

## Resources

- RStudio shiny tutorial: http://shiny.rstudio.com/tutorial/

- Useful if you want to use shiny on your own webserver: http://shiny.rstudio.com

- Latest updates: https://github.com/rstudio/shiny

- Shiny Mailing List: https://groups.google.com/forum/#!forum/shiny-discuss

In case of questions, check the tutorial first, then search the mailing list.



```{r include = FALSE}
library(shiny)
```

---
class: inverse
## Your Turn: A first example

- Download the file [`shiny.zip`](deps/shiny.zip), 

- unzip it into a folder,  

- put the folder into your working directory,

- and run the code below

```{r eval=F}
library(shiny)
runApp("shiny/01_Hello")
```
